Distill setup article added

### 2022-01-29 _posts/2022-01-29-distill-setup-article-added/distill-setup-article-added.Rmd
Text tweaks, build

---
title: "Distill setup article added"
description: |
  The first Distill how-to article is up.
author:
  - name: Steve Linberg
    url: https://slinberg.net
date: 2022-01-29
output:
  distill::distill_article:
    self_contained: false
---

@@

>>>>

---
title: "Distill setup article added"
description: |
  The first Distill how-to article is up in the Meta section.
author:
  - name: Steve Linberg
    url: https://slinberg.net
date: 2022-01-29
output:
  distill::distill_article:
    self_contained: false
---

@@

Note: the [source for this site](https://github.com/stevelinberg/distill-blog) can be found on github.
